Modelling the Co-evolution of Trade and Culture in the Roman market

### 2015-04-08 article.tex
slight modification

\newcommand{\memo}[2]{\textcolor{#1}{#2}}
\newcommand{\added}[2]{\textcolor{#1}{#2}}
%\renewcommand{\memo}[2]{} % uncomment in the final version
%\renewcommand{\added}[2]{#2} % uncomment in the final version
\newcommand{\todo}[1]{\memo{red}{TODO: #1\\}}
\newcommand{\simon}[1]{\memo{green}{Simon: #1\\}}
\newcommand{\jm}[1]{\memo{blue}{JM: #1\\}}
\newcommand{\xrc}[1]{\memo{orange}{XRC: #1\\}}
\newcommand{\new}[1]{\added{orange}{#1}}

@@

\title{Modelling the co-evolution of trade and culture in the Roman market}

@@

This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\cite{lake_trends_2014}. Next section defines the model, which is based on unbiased transmission mechanisms and simple exchange dynamics. Next, we define different experiments to explore the dynamics of the created model. Finally, the concluding remarks interpret the results and discuss further possibilities of the pesented model.

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ll|llll}
		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et al 2004}\\
			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
		N = 250	&0.004&1.53&0.03&1.54&0.02\\
			&0.016&1.57&0.02&1.57&0.01\\
			&0.064&1.66&0.01&1.67&0.01\\\hline
		N= 500	&0.004&1.50&0.02&1.53&0.03\\
			&0.016&1.55&0.03&1.61&0.04\\
			&0.064&1.78&0.08&1.81&0.10\\
	\end{tabular}
	\caption{Mean \& SD are calculate on 100 run.}
	\label{tab:mualpha}
\end{table}

\jm{Simon, do you have a comment on the table ? Like does it fit what is found in other articles ?}

@@

We observe that prices are indeed converging to the optimal prices which means that our innovation and imitation process are valid trade mechanisms. Notably, they produce results similar to the ones obtained in~\shortcite{gintis_emergence_2006}.

>>>>

\newcommand{\memo}[2]{\textcolor{#1}{#2}}
\newcommand{\added}[2]{\textcolor{#1}{#2}}
\renewcommand{\memo}[2]{} % uncomment in the final version
\renewcommand{\added}[2]{#2} % uncomment in the final version
\newcommand{\todo}[1]{\memo{red}{TODO: #1\\}}
\newcommand{\simon}[1]{\memo{green}{Simon: #1\\}}
\newcommand{\jm}[1]{\memo{blue}{JM: #1\\}}
\newcommand{\xrc}[1]{\memo{orange}{XRC: #1\\}}
\newcommand{\new}[1]{\added{orange}{#1}}

@@

\title{Modelling the Co-evolution of Trade and Culture in the Roman market}

@@

This work explores these co-evolutionary dynamics using a theoretical Agent-Based Model (ABM), a type of simulation particularly useful for studying non-linear dynamics in heterogeneous environments within an evolutionary perspective~\shortcite[3]{lake_trends_2014}. Next section defines the model, which is based on unbiased transmission mechanisms and simple exchange dynamics. Next, we define different experiments to explore the dynamics of the created model. Finally, the concluding remarks interpret the results and discuss further possibilities of the pesented model.

@@

\begin{table}[h]
	\centering
	\begin{tabular}{ll|llll}
		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et. al. 2004}\\
			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
		N = 250	&0.004&1.53&0.03&1.54&0.02\\
			&0.016&1.57&0.02&1.57&0.01\\
			&0.064&1.66&0.01&1.67&0.01\\\hline
		N= 500	&0.004&1.50&0.02&1.53&0.03\\
			&0.016&1.55&0.03&1.61&0.04\\
			&0.064&1.78&0.08&1.81&0.10\\
	\end{tabular}
	\caption{Mean \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
	\label{tab:mualpha}
\end{table}

We can see in this table that our results are close to those obtained by \shortcite[3]{bentley_random_2004}. In the same way \shortcite[3]{mesoudi_random_2009} also find similar value of $\alpha$ for similar values of $\mu$ and for the same number of agents. In the other hand it is difficult to know if the slight difference between those study are statistically significant as for the two previous studies the mean of $\alpha$ are computed using only between five runs, against 100 in our case.

@@

We observe that prices are indeed converging to the optimal prices which means that our innovation and imitation process are valid trade mechanisms. Notably, they produce results similar to the ones obtained in~\shortcite[3]{gintis_emergence_2006}.
